\section*{Professional Experience}
\cventry
{Ongoing}%
{Universe Guardian}%
{TARDIS Interdimensional Services}%
{Space-Time Continuum}%
{%
  \begin{itemize}%
    \item Chief defender of dimensional integrity and preservation of civilizations.
    \item Coordination of temporal and diplomatic interventions.
    \item Supervision of multi-planetary protection strategies.
    \item Maintenance of the delicate balance between parallel universes.
    \item Strategic oversight of interdimensional crisis management.
  \end{itemize}%
}{}%

\begin{cvsubentries}
  \cvsubentry
  {2005 - Present}%
  {Earth Intervention Specialist}%
  {Companion-Assisted Temporal Rescue Operations}%
  {Various Earth Locations}%
  {%
    \begin{itemize}
      \item Interventions against Dalek invasions and Cybermen attacks.
      \item Development of temporal intervention strategies minimizing disruptions.
      \item Training and support of human companions in temporal navigation.
      \item Emergency planetary defense protocols implementation.
      \item Diplomatic negotiations with advanced alien civilizations.
    \end{itemize}
  }{%
    \begin{description}%
      \item[Key Achievements:] Prevention of multiple global extinction events
    \end{description}%
  }

  \cvsubentry
  {Temporal Restoration Period}%
  {Multiversal Restoration Architect}%
  {Multiversal Preservation Agency}%
  {Parallel Universes}%
  {%
    \begin{itemize}
      \item Reconstruction and stabilization of damaged timelines.
      \item Critical interventions to prevent dimensional annihilation.
      \item Creation of quantum temporal healing techniques.
      \item Negotiation of complex inter-dimensional peace treaties.
      \item Advanced quantum entanglement restoration of fractured realities.
      \item Development of multi-dimensional crisis response protocols.
    \end{itemize}
  }{%
    \begin{description}%
      \item[Critical Missions:] Rescued 6 entire civilizations from temporal erasure
    \end{description}%
  }
\end{cvsubentries}

\cventry
{Time War Era}%
{Temporal Warfare Strategist}%
{Gallifreyan High Command}%
{Temporal Warfare}%
{%
  \begin{itemize}
    \item Advanced temporal warfare strategies against the Dalek Empire.
    \item Implementation of quantum encryption techniques.
    \item Responsible for the final resolution of the Time War.
    \item Development of advanced temporal shielding technologies.
    \item Strategic analysis of multi-dimensional conflict scenarios.
    \item Design of emergency temporal evacuation protocols.
  \end{itemize}
}{%
  \begin{description}%
    \item[Strategic Innovations:] Quantum Time Lock, Paradox Engine Development
  \end{description}%
}

\begin{cvsubentries}
  \cvsubentry
  {Prehistoric - Future Eras}%
  {Temporal Crisis Consultant}%
  {Intergalactic Stabilization Bureau}%
  {Multiple Dimensional Planes}%
  {%
    \begin{itemize}
      \item Consultation on critical temporal anomalies.
      \item Design of emergency intervention protocols.
      \item Principal expert witness at the Temporal High Court.
      \item Advanced temporal forensics and anomaly detection.
      \item Interdimensional conflict resolution and mediation.
      \item Development of quantum stability indexes for emerging civilizations.
    \end{itemize}
  }{%
    \begin{description}%
      \item[Key Interventions:] Prevention of 73 potential universal collapses
    \end{description}%
  }
\end{cvsubentries}
