\begin{cvsubentries}
 \cvsubentry
  {Pre-Time War}%
  {Quantum Exploration Specialist}%
  {Gallifreyan Temporal Exploration Division}%
  {Unmapped Cosmic Regions}%
  {%
    \begin{itemize}
      \item Pioneering expeditions into unmapped spatio-temporal regions.
      \item Establishment of first contact protocols.
      \item Scientific surveys of quantum-unstable regions.
      \item Mapping of quantum-entangled stellar phenomena.
      \item Development of advanced temporal navigation technologies.
      \item Comprehensive documentation of previously unknown cosmic ecosystems.
    \end{itemize}
  }{%
    \begin{description}%
      \item[Research Achievements:] Mapped 12 previously unknown quantum dimensions
    \end{description}%
  }
\end{cvsubentries}

\cventry
{Pre-Regeneration Periods}%
{Temporal Anthropologist}%
{Gallifreyan Observation Corps}%
{Multiple Civilizations}%
{%
  \begin{itemize}
    \item Extensive research on emerging civilizations.
    \item Development of non-intervention protocols.
    \item Pioneering techniques of cultural preservation and anthropological study.
    \item Advanced comparative analysis of technological and social development.
    \item Ethical framework design for temporal observation missions.
    \item Comprehensive documentation of civilizational life cycles.
  \end{itemize}
}{%
  \begin{description}%
    \item[Research Focus:] Comparative Civilizational Development, Temporal Sociology
  \end{description}%
}

\begin{cvsubentries}
  \cvsubentry
  {Early Gallifreyan Period}%
  {Temporal Physics Researcher}%
  {Time Lord Academy}%
  {Gallifrey}%
  {%
    \begin{itemize}
      \item Groundbreaking research in quantum temporal mechanics.
      \item Development of revolutionary time travel theories.
      \item Advanced studies in interdimensional physics.
      \item Prototype design for advanced TARDIS navigation systems.
      \item Theoretical modeling of temporal paradox resolution.
      \item Mentorship of emerging Time Lord scholars.
    \end{itemize}
  }{%
    \begin{description}%
      \item[Academic Achievements:] Youngest recipient of the Rassilon Temporal Innovation Award
    \end{description}%
  }

  \cvsubentry
  {Pre-Diplomatic Era}%
  {Xenopolitical Strategist}%
  {Gallifreyan Diplomatic Mission}%
  {Galactic Diplomatic Zones}%
  {%
    \begin{itemize}
      \item Negotiation of complex multi-species diplomatic agreements.
      \item Development of inter-species communication protocols.
      \item Mediation of high-stakes galactic conflicts.
      \item Strategic analysis of potential temporal interference risks.
      \item Design of diplomatic immunity frameworks for temporal travelers.
      \item Cultural exchange program development.
    \end{itemize}
  }{%
    \begin{description}%
      \item[Diplomatic Achievements:] Prevented 5 major interstellar conflicts
    \end{description}%
  }
\end{cvsubentries}
